paper1_results_figs_slimmed_50_rr

### 2016-06-27 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
change fig labels

             facet_grid( ~ seq_better_mixA0.5, labeller=as_labeller( c('0'='adaptive mix\nresistance slower','1'='sequential\nresistance slower'))) +

@@

             facet_grid( ~ mixA_not20pc_better_seq0.5, labeller=as_labeller( c('0'='adaptive mix\nresistance >20% slower','1'='adaptive mix\nresistance <20% slower'))) +

@@

             facet_grid( ~ seq_better_mix20.5, labeller=as_labeller( c('0'='mixture\nresistance slower','1'='sequential\nresistance slower'))) +

>>>>

             #facet_grid( ~ seq_better_mixA0.5, labeller=as_labeller( c('0'='adaptive mix\nresistance slower','1'='sequential\nresistance slower'))) +

             facet_grid( ~ seq_better_mixA0.5, labeller=as_labeller( c('0'='adaptive mix\ntime to resistance\n longer','1'='sequential\ntime to resistance\n longer'))) +

@@

             facet_grid( ~ mixA_not20pc_better_seq0.5, labeller=as_labeller( c('0'='adaptive mix\ntime to resistance\n >20% longer','1'='adaptive mix\ntime to resistance\n >20% longer'))) +

@@

             facet_grid( ~ seq_better_mix20.5, labeller=as_labeller( c('0'='mixture\ntime to resistance\nlonger','1'='sequential\ntime to resistance\nlonger'))) +
